Scagnostics and Projection Pursuit

### 2018-02-01 Draft/Draft.Rmd
Small study to check dependence on gminus2 variable.

Additions to the standard scagnostics measures have been implemented in the package mbgraphics, based on splines (spline2d) and distance correlation (dcor2d).
Give definitions here..
We repeat the study from before, we first test in Figure ADDREF the behaviour of the index values over 100 interpolated projections that are randomly selected via the grand tour algorithm (the same projections as considered above).
Note that here the measures are calculated on non-binned data.
The general behaviour seems similar to the scagnostics monotonic index.
The observed behaviour is smooth (much in contrast to the behaviour of the scagnostics measures) and we next test the behaviour in a guided tour, comparing again also the first and final projection. (which index to select, will try both below...)
It seems they both maximise correlation, this might not be too useful?
```{r mbgraphics-indices, fig.height=3, fig.cap="(ref:mbgraphics-indices)"}
```
```{r guided-spline2d, include=FALSE}
```
```{r guided-spline2d-plot, fig.height=3, fig.cap="(ref:guided-spline2d-plot)"}
```
```{r guided-dcor2d, include=FALSE}
```
```{r guided-dcor2d-plot, fig.height=3, fig.cap="(ref:guided-dcor2d-plot)"}
```

@@

>>>>

Additions to the standard scagnostics measures have been implemented in the package mbgraphics, based on splines (spline2d) and distance correlation (dcor2d).
Give definitions here..
We repeat the study from before, we first test in Figure ADDREF the behaviour of the index values over 100 interpolated projections that are randomly selected via the grand tour algorithm (the same projections as considered above).
Note that here the measures are calculated on non-binned data.
The general behaviour seems similar to the scagnostics monotonic index.
The observed behaviour is smooth (much in contrast to the behaviour of the scagnostics measures) and we next test the behaviour in a guided tour, comparing again also the first and final projection. (which index to select, will try both below...)
It seems they both maximise correlation, this might not be too useful?
Seems like [,1] basically -[,2] in the final projection (except for [7,])?
probably we see only structure of gminus2 variable, which has very narrow peak, only few outlying points
is there a better way of transforming it to spread out the structure?

```{r mbgraphics-indices, fig.height=3, fig.cap="(ref:mbgraphics-indices)"}
```
```{r guided-spline2d, include=FALSE}
```
```{r guided-spline2d-plot, fig.height=3, fig.cap="(ref:guided-spline2d-plot)"}
```
```{r guided-dcor2d, include=FALSE}
```
```{r guided-dcor2d-plot, fig.height=3, fig.cap="(ref:guided-dcor2d-plot)"}
```

@@

```{r gminus2-box, fig.height=3}
```

```{r guided-dcor2d-no-gminus2, include=FALSE}
```
```{r guided-dcor2d-plot-no-gminus2, fig.height=3, fig.cap="(ref:guided-dcor2d-plot)"}
```

### 2018-02-01 Draft/Draft.tex
Small study to check dependence on gminus2 variable.

Additions to the standard scagnostics measures have been implemented in
the package mbgraphics, based on splines (spline2d) and distance
correlation (dcor2d). Give definitions here.. We repeat the study from
before, we first test in Figure ADDREF the behaviour of the index values
over 100 interpolated projections that are randomly selected via the
grand tour algorithm (the same projections as considered above). Note
that here the measures are calculated on non-binned data. The general
behaviour seems similar to the scagnostics monotonic index. The observed
behaviour is smooth (much in contrast to the behaviour of the
scagnostics measures) and we next test the behaviour in a guided tour,
comparing again also the first and final projection. (which index to
select, will try both below\ldots{}) It seems they both maximise
correlation, this might not be too useful?

@@

>>>>

Additions to the standard scagnostics measures have been implemented in
the package mbgraphics, based on splines (spline2d) and distance
correlation (dcor2d). Give definitions here.. We repeat the study from
before, we first test in Figure ADDREF the behaviour of the index values
over 100 interpolated projections that are randomly selected via the
grand tour algorithm (the same projections as considered above). Note
that here the measures are calculated on non-binned data. The general
behaviour seems similar to the scagnostics monotonic index. The observed
behaviour is smooth (much in contrast to the behaviour of the
scagnostics measures) and we next test the behaviour in a guided tour,
comparing again also the first and final projection. (which index to
select, will try both below\ldots{}) It seems they both maximise
correlation, this might not be too useful? Seems like {[},1{]} basically
-{[},2{]} in the final projection (except for {[}7,{]})? probably we see
only structure of gminus2 variable, which has very narrow peak, only few
outlying points is there a better way of transforming it to spread out
the structure?

@@

\begin{center}\includegraphics[width=\textwidth]{figure/gminus2-box-1} \end{center}

\end{CodeChunk}

\begin{CodeOutput}
            [,1]        [,2]
[1,]  0.48848925 -0.37880896
[2,]  0.09066938  0.10280711
[3,]  0.54333417  0.80184027
[4,] -0.05279536  0.00809942
[5,] -0.47070661  0.10044669
[6,] -0.48331484  0.43912584
\end{CodeOutput}
\begin{figure}

{\centering \includegraphics[width=\textwidth]{figure/guided-dcor2d-plot-no-gminus2-1} \includegraphics[width=\textwidth]{figure/guided-dcor2d-plot-no-gminus2-2} \includegraphics[width=\textwidth]{figure/guided-dcor2d-plot-no-gminus2-3}

\caption[(ref:guided-dcor2d-plot)]{(ref:guided-dcor2d-plot)}\label{fig:guided-dcor2d-plot-no-gminus2}
\end{figure}
\end{CodeChunk}
